Implementing simplified INLA into `aghq`

### 2022-10-20 src/dev_sinla/sinla.Rmd
Debug aghq::aghq (see aghq/issues/6)

```{r}
# h$he <- function(theta) numDeriv::jacobian(h$gr, theta, method = "Richardson")
# quad <- aghq::aghq(ff = h, k = 1, startingvalue = h$par)
```

@@

In Section \@ref(full-laplace) we directly calculate the Laplace approximation to $\int p(x, y, \theta) \text{d} \theta_{-i}$.
Suppose that
$$
x \sim \mathcal{N}(\mu(\theta), Q(\theta)^{-1})
$$
then by the conditional distributions of a multivariate Gaussian distribution $x_{-i} \, | \, x_i$ is Gaussian with mean
$$
\mu(\theta)_{-i} + \Sigma(\theta)_{-i, i} \Sigma(\theta)^{-1}_{i, i} (x_i - \mu (\theta)_i) (\#eq:conditionalmean)
$$
and precision matrix
$$
Q(\theta)_{-i, -i}
$$

>>>>

```{r}
h$he <- function(theta) numDeriv::jacobian(h$gr, theta, method = "Richardson")
quad <- aghq::aghq(ff = h, k = 3, startingvalue = c(0, 0), control = aghq::default_control_tmb())
quad$normalized_posterior$lognormconst
```

@@

In Section \@ref(full-laplace) we directly calculate the Laplace approximation to $\int p(x, y, \theta) \text{d} \theta_{-i}$.
Suppose that
$$
x \sim \mathcal{N}(\mu(\theta), Q(\theta)^{-1})
$$
then by the conditional distributions of a multivariate Gaussian distribution $x_{-i} \, | \, x_i$ is Gaussian with mean
$$
\mu(\theta)_{-i} + \Sigma(\theta)_{-i, i} \Sigma(\theta)^{-1}_{i, i} (x_i - \mu (\theta)_i) (\#eq:conditionalmean)
$$
and precision matrix
$$
Q(\theta)_{-i, -i} (\#eq:conditionalprecision)
$$
